\section{INTRODUCTION TO PROJECT}

This is an attempt to create a project AUTOMOBILE FINANCE MANAGEMENT through which will show
all details of the Vehicles sold and the owners details. This project can make the tedious and mistake prone
job easier and faster. It can be used both in top-level and bottom-level management for daily
operation.\newline
This project also contains the details of the persons who took the loan for buying a vehicle.It also updates the details of EMI's monthly paid by the person.\newline
There are two users to system:
\newline
\begin{itemize}
\item ADMIIN\newline
A Admin can perform various functions:
\begin{itemize}
\item Login
\item Entering of details
\item Search
\item Update
\item Reset
\item Use Utilities
\end{itemize}
\item HEAD\newline
A Head can perform various functions:
\begin{itemize}
\item Login
\item Entering of details
\item Search
\item Update
\item Reset
\item Use Utilities
\end{itemize}
\end{itemize}

\section{PROJECT CATEGORY}
AUTOMOBILE FINANCE MANAGEMENT is a computer application which is used to manage the data of Automobile Companies.

\section{OBJECTIVES}
\begin{itemize}
\item To handle the manual handling and even the workload of the employees of the company by introducing a change in the existing many software system to a single software implementation.
\item To save time and cost of the employees and company by providing information very efficiently and easily.
\item To have a proper record of the vehicles coming to toll plaza and having a list and record of that vehicles.
\item To provide a system with proper recovery of data, in case lost, through a proper backup     provided.
\item To provide the head with the basic utilities like file choosers, web browser, account settings and backup within the system for the proficient work management of the company.
\end{itemize}

\section{EXISTING SYSTEM}
In existing system all the data is recorded in files. In this method time and manual work is required. Maintaining critical information in the files and manuals is full of risk and a tedious process.
Some of the negative aspects of the existing system that it is prone to corruption by unauthorized users. Securing of manual system is not fully guaranteed. Inaccuracy can be expected.
Data can get easily scratched. Techniques used are more complicated.Proper techniques are not
exposed, so the functioning is intricate.To overcome these, the proposed system has been suggested.

\section{PROPOSED SYSTEM}
This application enables the employees to manage the data in computers more effectively and accurately.
It saves the time as in this project an employee can search, update, reset or insert data by just clicking a single button.
In this project employee need not to devote extra time in finding the records, employee just need to click a single button to access the data.
