
\section{PAGES}  
\begin{itemize}
\item Enter Login Details: LoginAs, Uder ID and Password
\item Master \newline
Definition of Master : All the information your company needs  is stored in a data record in the master data, sorted by various different criteria. You can enter and change most of the data in master data by head . In master  we have all Employee  details which includes their name, employee id ,address, phone number,email etc. and   Vehicle details which includes product id, vehicle type , vehicle name ,model,price .
\newline
Master Data Module contains various sections:	
\begin{itemize}
\item Employee Details
\item Vehicle Detail
\end{itemize}
\item Transaction\newline
Definition of Transaction: It includes enquiry,request, verification, approval and deposit information of the vehicle .\newline
\begin{itemize}
\item Enquiry:  In this section, customer enquiry details are there. We can select the vehicle type which enables to select vehicle name and it automatically displays vehicle model.
\item Request: It consist of request form which contains  the payment record including instalments.
\item Verification: It includes verification of the customer details.
\item Approval: After the verification is successfully over, then request is approved.
\item Deposit: It consist of deposit details like the mode of payment, taxes, due date etc.
\end{itemize}
\item Listing \newline
Definition of List of Data: This section provides the list of data. The List of data includes all the data of a particular section.
\begin{itemize}
\item Enquiry
\item Enquiry Details
\item Request
\item Request Details
\item Verification
\item Approval
\item Deposit
\item Employee Details
\item Vehicle Details
\end{itemize}
\item Settings\newline
 Settings: This section provide us account settings, File Chooser, Web Browser and Backup. Account settings and backup only access by head.\newline
Settings Module contains various sections:
\begin{itemize}
\item Account Settings: In Account Settings, System Head can Create a new user account and can change the password of existing accounts in the system. Change Password can be used if in any case user forget password of his account.
\item File Chooser: A file chooser  is a computer program that provides a user interface to work with file systems. User can access any type of document (like pdf,mp3,jpg).
\item Web Browser: A file chooser  is a computer program that provides a user interface to work with file systems. User can access any type of document (like pdf,mp3,jpg).

\end{itemize}
\end{itemize}




